---
output: pdf_document
fontsize: 12pts
geometry: margin = 1in
# indent: true # this works
# header-includes:
#    - \setlength\parindent{24pt}  # this works too, but I'm gonna indent manually with 4 spaces
# nope, 4 spaces indents are not recognized, they do something else
linestretch: 1
header-includes:
    - \usepackage[left]{lineno}
    # - \linenumbers
---
```{r echo = FALSE, warning=FALSE}
# install.packages("knitr", "kableExtra")
# devtools::install_github(repo = "haozhu233/kableExtra")
x <- lapply(c("knitr", "kableExtra", "ape"), library, character.only = TRUE)
```

```{r echo = FALSE, results = 'asis', warning=FALSE}
table_files <- paste0(
  "~/GoogleDrive/GoogleDrive.7nov2014/Analysis/Nuria/agave_bat_diversification/2_Analyses/",
  c("agavaceae.crown.whole_2016.10.19.xls",
  paste0("1shift_NuriAgaves/",
  c("1shift_BBcladeA_2016.10.19.xls",
  "1shift_cladeA_stem_2016.10.19.xls",
  "1shift_BBcladeA1_2016.10.20.xls",
  "1shift_cladeA1_stem_2016.10.20.xls",
  "1shift_BBcladeA2_2016.10.20.xls",
  "1shift_cladeA2_stem_2016.10.20.xls",
  "1shift_BBcladeB_2016.10.20.xls",
  "1shift_cladeB_stem_2016.10.20.xls",
  "1shift_BBcladeB1_2016.10.21.xls",
  "1shift_cladeB1_stem_2016.10.21.xls",
  "1shift_BBcladeB2_2016.10.21.xls",
  "1shift_cladeB2_stem_2016.10.21.xls")),
  paste0("2shifts_NuriAgaves/",
  c("2shift_BBcladeA_B1_2016.10.23.xls",
  "2shift_BBcladeA_B2_2016.10.23.xls",
  "2shift_BBcladeA1_A2_2016.10.22.xls",
  "2shift_BBcladeA1_B1_2016.10.23.xls",
  "2shift_BBcladeA1_B2_2016.10.23.xls",
  "2shift_BBcladeA2_B1_2016.10.24.xls",
  "2shift_BBcladeA2_B2_2016.10.24.xls",
  "2shift_BBcladeB_A1_2016.10.22.xls",
  "2shift_BBcladeB_A2_2016.10.23.xls",
  "2shift_BBcladeB1_B2_2016.10.26.xls")),
  paste0("3shifts_NuriAgaves/",
  c("3shift_BBcladeA1_A2_B1_2016.10.26.xls",
  "3shift_BBcladeA1_A2_B2_2016.10.26.xls",
  "3shift_BBcladeA1_B1_B2_2016.10.26.xls",
  "3shift_BBcladeA2_B1_B2_2016.10.26.xls"))
  )
)
my_table_format <- function(tt){
  res <- format.data.frame(tt, digits = 4, nsmall = 4, justify = "none")
  return(res)
}
all_tables <- vector(mode = "list")
for (i in table_files){
  PAR <- read.table(i, header=TRUE)
  names(PAR)[names(PAR)=="LH"] <- "logLH"
  names(PAR)[names(PAR)=="alfa"] <- "alpha"
  PAR <- PAR[order(PAR$logLH, decreasing = TRUE),c("model", "lambda", "alpha", "mu", "beta", "logLH", "AICc", "deltaAICc")]
  # neg <- PAR$lambda <0 
  # PAR$lambda <- abs(PAR$lambda)
  # PAR$alpha[neg] <- -1*PAR$lambda[neg]
  # neg <- PAR$mu <0 
  # PAR$mu <- abs(PAR$mu)
  # PAR$beta[neg] <- -1*PAR$beta[neg]
  # my_func <- function(x){
  #   rr <- abs(x) > 1
  #   rr <- rr[!is.na(rr)]
  #   x[rr] <- round(x[rr], digits = 4)
  #   x[!rr] <- round(x[!rr], digits = 5)
  #   return(x)
  # }
  # x1 <- lapply(PAR[,c("lambda", "alpha", "mu", "beta", "LH", "AICc", "deltaAICc")], my_func)
  # PAR <- cbind(PAR$model, data.frame(x1))
  all_tables <- c(all_tables, list(my_table_format(PAR)))
}
# name the tables so it's easier to call them later:
table_names <- regmatches(table_files, regexpr(pattern = "_.{0,2}clade.*_2", table_files))
table_names <- sub("_", "", table_names)
table_names <- sub("_2", "", table_names)
table_names <- sub("_s.*", "", table_names)
table_names <- c("whole", table_names)
names(all_tables) <- table_names
# col_width <- paste0(c(2, 1.5, 1.5, 2, 2, 1.5, 1.5, 1.5), "cm")  # not using this format at the end

# source('~/Google Drive/GoogleDrive.7nov2014/Analysis/Diversification/Morlon2011&Condamine/jointAIC_2016.10.23_V6.R')
jointAIC6 <- function(jointLH, p, nobs){
	JointAICc <-  2*jointLH*(-1) + (2*p) * (nobs/(nobs-p-1))
	return(JointAICc)
}

agave <- ape::read.nexus("~/GoogleDrive/GoogleDrive.7nov2014/Analysis/Nuria/agave_bat_diversification/1_Data/Agave5_14Nov13.TreeAnnOut")

clade_code_names <- c("cladeA", "cladeA1", "cladeA2", "cladeB", "cladeB1", "cladeB2")
clade_names <- list(cladeA = "_Agave s.l._ + _Furcraea_/_Beschorneria_",
  cladeA1 = "_Agave s.l._",
  cladeA2 = "_Furcraea_/_Beschorneria_",
  cladeB = "_Yucca_ + _Hesperoyucca_/_Hesperaloe_",
  cladeB1 = "_Yucca_",
  cladeB2 = "_Hesperoyucca_/_Hesperaloe_")

cladeA <-  expression(~italic(Agave~s.l.)*"+"* italic(Furcraea*"/"*Beschorneria))
# clade_names <- list(cladeA = expression(~italic(Agave~s.l.)*"+"* italic(Furcraea*"/"*Beschorneria)),
#   cladeA1 = "_Agave s.l._",
#   cladeA2 = "_Furcraea_/_Beschorneria_",
#   cladeB = "_Yucca_ + _Hesperoyucca_/_Hesperaloe_",
#   cladeB1 = "_Yucca_",
#   cladeB2 = "_Hesperoyucca_/_Hesperaloe_")

crown_nodes <- c(57, 58, 88, 51, 54, 52)
stem_nodes <- sapply(crown_nodes, function(x) phytools::getParent(agave, x))
stem_times <- sapply(stem_nodes, function(x)   ape::branching.times(agave)[as.character(x)])
names(stem_times) <- clade_code_names
clade_trees <- lapply(crown_nodes, function(x) ape::extract.clade(agave, x))
# cladeA <- extract.clade(agave, 57) # Agave s.l. + Furcraea/Beschorneria
# cladeA1 <- extract.clade(agave, 58)  # Agave s.l.
# cladeA2 <- extract.clade(agave, 88) # Furcraea/Beschorneria
# cladeB <- extract.clade(agave, 51) # Yucca + Hesperoyucca/Hesperaloe
# cladeB1 <- extract.clade(agave, 54) # Yucca
# cladeB2 <- extract.clade(agave, 52) # Hesperoyucca/Hesperaloe
names(clade_trees) <- clade_code_names

source("plot.div.functions.R")
plot.divratett.all <- function(rates, times = c(10, 0), 
                           models = "all", color = NULL, 
                           add_legend = TRUE, opar) {
  if (models == "all"){
    models <- rates$model[order(rates$logLH, decreasing = T)]
  }
  if(is.null(color)){
    color <- c("gray", "darkgreen", "lightgreen", "blue", "lightblue", "purple", "plum1")
    names(color) <- c("BconsDcons", "BexpDcons", "BlinDcons", "BconsDexp", "BconsDlin", "BexpDexp", "BlinDlin")
  }
  for(j in models){
    f <- match.fun(FUN = paste0("plot.divratett.", j))
    f(rates = rates, times = times, color = color)
  }
  if(add_legend){
    par(opar)
    opar = par(oma = c(0,0,0,0), mar = c(0,0,0,0), new = TRUE)
    legend(legend = rev(models), col = rev(color[models]), 
           # lty = "solid", lwd = 2,
           pch =16,
         bty = "n", xpd = T, cex = 0.6, title = "models", 
         x = "right")
    par(opar)
  }
}
plot.divratett <- function(rates, span = c(10, 0), 
                           models = "all", color = NULL, add_legend = TRUE,
                           x_lim = span*1.1, y_lim = c(-1, 1)) {
  # opar = par(oma = c(0,0,0,3))
  opar <- par(oma = c(0, 0, 1.5, 4), mai = c(0.5, 0.5, 0.1, 0), mar = c(2, 2.5, 0, 0))  # para leyenda mas abajo, cambiar oma = c(0, 0, 0, 4)
  plot(x=NULL, main=NULL, xlab="", ylab="", 
       xlim = x_lim, ylim= y_lim, axes=FALSE)
  # box("outer", lty="solid", col="green")
  # box("inner", lty="solid", col="red")
  # box("figure",lty="solid", col="blue")
  axis(2, at= seq(y_lim[1], y_lim[2], 1), labels=T, las =1, 
       cex.axis =0.8, mgp=c(1,0.8,0))
  axis(1, pos= y_lim[1], cex.axis =0.8, mgp=c(1,0.5,0))
  mtext(text = "Time (Myr)", side=1, outer=F, cex =0.8, 
        at = max(x_lim)/2, line = 1)

  abline(h=0, col="gray")
  plot.divratett.all(rates = rates, times = span, models = models,
                     color = color, add_legend = add_legend, opar = opar)
  mtext(text = "Species per Myr", side=2, line=-1, outer=T, cex =0.8)
}

```

## Flores-Abreu et al. 2018. Tempo and mode in coevolution of _Agave sensu lato_ (Agavoideae, Asparagaceae) and its bat pollinators, Glossophaginae (Phyllostomidae)
## Supplementary Material

In all tables and figure legends, models are ordered in decreasing log Likelihood (logLH) value, 
AICc = corrected Akaike Information Criterion, 
n = number of tips as number of observations for AICc computation, and
deltaAICc = AICc difference with lowest AICc value.

In some cases, model fitting analyses result in negative speciation and/or extinction values. The likelihood function is set up like that to allow negative diversification rates (Hélène Morlon, pers. comm.). 

# No shifts in diversification dynamics evaluated with RPANDA

### Table S1. Agavoideae from crown age.

```{r echo = FALSE, results = 'asis', warning=FALSE, fig.align = "left", fig.height= 3}
# table_captions <- vector(mode = "list")
# for (i in 1:21){
#   table_captions <- c(table_captions, 
#   paste0("Table S", i, ".", "diversification dynamics evaluated with RPANDA."))
# }
print(kable(all_tables$whole, caption = NULL, row.names = FALSE, booktabs = T) # %>%
            # kable_styling(full_width = TRUE)
)
y_limA <- rep(-1, 27)
names(y_limA) <- c("1", "2a", "2b", "3a", "3b", "4a", "4b", "5a", "5b", "6a", "6b", "7a", "7b", as.character(8:21))
y_limB <- c(3, 1, 2, 1, 2, 2, 1, 2, 1, 2, 1, 2, rep(1, 7), rep(2, 4), 1, 1.5, 1, 2)
names(y_limB) <- names(y_limA)
cat("\n", "### Figure S1. Agavoideae  diversification rate through time plots. Rates estimated from crown group age.", "\n")
# rates is a data.frame or list
plot.divratett(rates = all_tables$whole, span = c(stem_times[1],0), x_lim = c(16,0), y_lim = c(y_limA[1], y_limB[1]))
  # box("outer", lty="solid", col="green")
  # box("inner", lty="solid", col="red")
  # box("figure",lty="solid", col="blue")
```

# Models of 1 shift in diversification dynamics evaluated with RPANDA

```{r echo = FALSE, results = 'asis', warning=FALSE, fig.align = "center", fig.height= 4}
# check out for next step https://stackoverflow.com/questions/36674824/use-loop-to-generate-section-of-text-in-rmarkdown
table_title <- "
### Table S%s. 1 shift in %s from stem age.

"

figure_title <- "
### Figure S%s. 1 shift in %s diversification rate through time plots. 

"

n_clades <- sapply(clade_trees, Ntip)
n_backbone <- Ntip(agave) - n_clades
bb_title <- paste0("A. Backbone (n = ", n_backbone, ")")
clade_title <- paste0("B. Shift in clade (n = ", n_clades, ")")
fig_clade_title <- paste0("B. %s (n = ", n_clades, ")")

count <- 1
for (j in seq(2,13,2)) {
  # estimating joint LH and AICc
  bb_models <- which(as.numeric(all_tables[[j]]$deltaAICc) <= 2)
  clade_models <- which(as.numeric(all_tables[[j+1]]$deltaAICc) <= 2)
  global_models <- expand.grid(backbone= bb_models, 
                               clade=clade_models)
  joint_logLH <- as.numeric(all_tables[[j]]$logLH[global_models$backbone]) + as.numeric(all_tables[[j + 1]]$logLH[global_models$clade])
  bb_extra_par <- sapply(all_tables[[j]][, c("alpha", "beta")],
                         function(x) !grepl("NA", x))
  clade_extra_par <- sapply(all_tables[[j+1]][, c("alpha", "beta")],
                            function(x) !grepl("NA", x))
  p_sum <- function(x){
    if(length(x) < 3) {
      res <- sum(x)
    } else {
      res <- rowSums(x)
    }
    return(res)
  }
  p_all_models <- 4 + p_sum(bb_extra_par[global_models$backbone,]) + p_sum(clade_extra_par[global_models$clade,])  # we always have at least 4 parameters in the simplest BconsDcons model (for both backbone and clade); we just need to sum the extra two parameters of each case
  joint_AICc <- sapply(joint_logLH, jointAIC6, p_all_models, Ntip(agave))
  if(!is.null(dim(joint_AICc))){
  joint_AICc <- sapply(joint_logLH, jointAIC6, p_all_models, Ntip(agave))[1,]    
  }
  ee <- rep("", length(joint_AICc))
  global_table <- data.frame(model = ee, lambda = ee, alpha = ee,
    Backbone = all_tables[[j]]$model[bb_models], 
    Clade = all_tables[[j+1]]$model[clade_models], 
    logLH = joint_logLH, 
    AICc = joint_AICc, 
    deltaAICc = joint_AICc - min(joint_AICc)
  )
  global_table <- global_table[order(global_table$logLH, decreasing = T),]
  
  cat(sprintf(table_title, count+1, clade_names[[count]]))
  
  print(kable(rbind(all_tables[[j]], all_tables[[j+1]]),
        caption = NULL, row.names = FALSE, booktabs = T) %>%
          group_rows(bb_title[count], 1, 7)  %>%
          group_rows(clade_title[count], 
                    8, 14) # %>%
                    # kable_styling(full_width = TRUE)
  )
  cat("**Global model**", "\n")
  global_table <- my_table_format(global_table)
  print(kable(global_table, 
        caption = NULL, row.names = FALSE, booktabs = T) %>%
          row_spec(0, color = c(rep("white", 3), rep("black", 5))) # %>%
          # kable_styling(full_width = TRUE)
  )
  cat("\n\n")
  cat(sprintf(figure_title, count+1, clade_names[[count]]))
  # cat(bb_title[count])
  # cat(sprintf(fig_clade_title[count], clade_names[[count]]))
  pl <- paste0("figureS", count+1, "A.pdf") 
  pdf(pl, height = 2.5, width = 3)
  # par(mfrow = c(2, 1))
  # layout(matrix(c(1,1),1, 2,byrow = F))
  plot.divratett(rates = all_tables[[j]], 
                 span = c(stem_times[1],0), 
                 x_lim = c(16,0), y_lim = c(y_limA[paste0(count+1, "a")], y_limB[paste0(count+1, "a")]))
  # title(bb_title[count])
  mtext(bb_title[count], side = 3, line=-0.5, cex= 0.8, col="black", outer = F, at = 16.5, font = 1)
  # box("outer", lty="solid", col="green")
  # box("inner", lty="solid", col="red")
  # box("figure",lty="solid", col="blue")
  dev.off()
  #https://github.com/yihui/knitr/issues/1260
  cat("![](",pl,")")
  cat(" ")
  # cat(sprintf(fig_clade_title[count], clade_names[[count]]))
  pl <- paste0("figureS", count+1, "B.pdf")
  pdf(pl, height = 2.5, width = 3)

  plot.divratett(rates = all_tables[[j+1]], 
                 span = c(stem_times[names(all_tables[j+1])],0), 
                 x_lim = c(16,0), y_lim = c(y_limA[paste0(count+1, "b")], y_limB[paste0(count+1, "b")]))
  mtext(clade_title[count], side = 3, line=-0.5, cex=0.8, col="black", outer = F, at = 15.7, font = 1)
# box("outer", lty="solid", col="green")
  # box("inner", lty="solid", col="red")
  # box("figure",lty="solid", col="blue")
  # mtext(clade_title[count], NORTH<-3, at=5, line=0.25, cex=1.2, col="black")
  dev.off()
  cat("![](",pl,")")
  # include_graphics(paste0("figureS", count+1, "A.pdf"))
  # include_graphics(paste0("figureS", count+1, "B.pdf"))
  cat("\n\\pagebreak\n")

  count <- count + 1
  }


cat("\n# Models of 2 shifts in diversification dynamics evaluated with RPANDA\n")

# check out for next step https://stackoverflow.com/questions/36674824/use-loop-to-generate-section-of-text-in-rmarkdown
table_title <- "
### Table S%s. A shift in %s and another in %s, both from stem age.

"
figure_title <- "
### Figure S%s. One shift in %s and another in %s backbone diversification rate through time plot. 

"

two_shift <- t(combn(clade_code_names, 2))
two_shift <- two_shift[-c(1:3,13:14),]  # remove clade combinations that were not tested
two_shift <- cbind(table_names[c(14,15,16,21,17,18,22,19,20,23)], two_shift)
n_clades <- data.frame(clade1 = sapply(two_shift[,2], function(x) Ntip(clade_trees[[x]])), clade2 = sapply(two_shift[,3], function(x) Ntip(clade_trees[[x]])) )

n_backbone <- Ntip(agave) - rowSums(n_clades)
bb_title <- paste0("A. Backbone (n = ", n_backbone, ")")
clade1_title <- paste0("B. Shift in clade 1 (n = ", n_clades[,1], ")")
clade2_title <- paste0("C. Shift in clade 2 (n = ", n_clades[,2], ")")

for (j in 1:nrow(two_shift)) {
  # estimating joint LH and AICc
  bb_models <- which(as.numeric(all_tables[[two_shift[j,1]]]$deltaAICc) <= 2)
  clade1_models <- which(as.numeric(all_tables[[two_shift[j,2]]]$deltaAICc) <= 2)
  clade2_models <- which(as.numeric(all_tables[[two_shift[j,3]]]$deltaAICc) <= 2)
  global_models <- expand.grid(backbone= bb_models,
                               clade1= clade1_models,
                               clade2= clade2_models)
  joint_logLH <- as.numeric(all_tables[[two_shift[j,1]]]$logLH[global_models$backbone]) + as.numeric(all_tables[[two_shift[j,2]]]$logLH[global_models$clade1]) + as.numeric(all_tables[[two_shift[j,3]]]$logLH[global_models$clade2])
                                                                                  # get number of extra parameters for each model:
  bb_extra_par <- sapply(all_tables[[two_shift[j,1]]][, c("alpha", "beta")],
                         function(x) !grepl("NA", x))
  clade1_extra_par <- sapply(all_tables[[two_shift[j,2]]][, c("alpha", "beta")],
                            function(x) !grepl("NA", x))
  clade2_extra_par <- sapply(all_tables[[two_shift[j,3]]][, c("alpha", "beta")],
                            function(x) !grepl("NA", x))
  p_sum <- function(x){
    if(length(x) < 3) {
      res <- sum(x)
    } else {
      res <- rowSums(x)
    }
    return(res)
  }
# we always have at least 6 parameters in the simplest BconsDcons model (for backbone and 2 clades); we just need to sum the extra two parameters of each case:
  p_all_models <- 6 +
                  p_sum(bb_extra_par[global_models$backbone,]) +
                  p_sum(clade1_extra_par[global_models$clade1,])  +
                  p_sum(clade2_extra_par[global_models$clade2,])
  joint_AICc <- sapply(joint_logLH, jointAIC6, p_all_models, Ntip(agave))
  if(!is.null(dim(joint_AICc))){
    joint_AICc <- sapply(joint_logLH, jointAIC6, p_all_models,
                         Ntip(agave))[1,]
  }
  ee <- rep("", length(joint_AICc))  # just to generate empty columns
  global_table <- data.frame(model = ee, lambda = ee,
    Backbone = all_tables[[two_shift[j,1]]]$model[global_models$backbone],
    Clade1 = all_tables[[two_shift[j,2]]]$model[global_models$clade1],
    Clade2 = all_tables[[two_shift[j,3]]]$model[global_models$clade2],
    logLH = joint_logLH,
    AICc = joint_AICc,
    deltaAICc = joint_AICc - min(joint_AICc)
  )
  global_table <- global_table[order(global_table$logLH, decreasing = T),]

  cat(sprintf(table_title, count+1,
              clade_names[two_shift[j,2]], clade_names[two_shift[j,3]]))

  print(kable(rbind(all_tables[[two_shift[j,1]]],
                    all_tables[[two_shift[j,2]]],
                    all_tables[[two_shift[j,3]]]),
        caption = NULL, row.names = FALSE, booktabs = T) %>%
          group_rows(bb_title[j], 1, 7) %>%
          group_rows(clade1_title[j], 8, 14) %>%
          group_rows(clade2_title[j], 15, 21) # %>%
                    # kable_styling(full_width = TRUE)
  )
  cat("**Global model**", "\n")
  global_table <- my_table_format(global_table)
  print(kable(global_table,
        caption = NULL, row.names = FALSE, booktabs = T) %>%
          row_spec(0, color = c(rep("white", 2), rep("black", 6)))
  )
  cat("\n\n")
  cat(sprintf(figure_title, count+1, 
              clade_names[two_shift[j,2]], clade_names[two_shift[j,3]]))
  plot.divratett(rates = all_tables[[two_shift[j,1]]], 
                 span = c(stem_times[1],0), 
                 x_lim = c(16,0), y_lim = c(y_limA[as.character(count+1)], y_limB[as.character(count+1)]))
  cat("\n\\pagebreak\n")
  count <- count + 1

}

cat("\n# Models of 3 shifts in diversification dynamics evaluated with RPANDA\n")

table_title <- "
### Table S%s. Three shifts in %s, %s and in %s, from clade stem age.

"
figure_title <- "
### Figure S%s. Shifts in %s, %s and %s backbone diversification rate through time plot. 

"

three_shift <- t(combn(clade_code_names[-c(1,4)], 3))
three_shift <- cbind(table_names[24:27], three_shift)
n_clades <- data.frame(clade1 = sapply(three_shift[,2], function(x) Ntip(clade_trees[[x]])), clade2 = sapply(three_shift[,3], function(x) Ntip(clade_trees[[x]])), clade3 = sapply(three_shift[,4], function(x) Ntip(clade_trees[[x]])) )

n_backbone <- Ntip(agave) - rowSums(n_clades)
bb_title <- paste0("A. Backbone (n = ", n_backbone, ")")
clade1_title <- paste0("B. Shift in clade 1 (n = ", n_clades[,1], ")")
clade2_title <- paste0("C. Shift in clade 2 (n = ", n_clades[,2], ")")
clade3_title <- paste0("C. Shift in clade 3 (n = ", n_clades[,3], ")")

for (j in 1:nrow(three_shift)) {
  # estimating joint LH and AICc
  bb_models <- which(as.numeric(all_tables[[three_shift[j,1]]]$deltaAICc) <= 2)
  clade1_models <- which(as.numeric(all_tables[[three_shift[j,2]]]$deltaAICc) <= 2)
  clade2_models <- which(as.numeric(all_tables[[three_shift[j,3]]]$deltaAICc) <= 2)
  clade3_models <- which(as.numeric(all_tables[[three_shift[j,4]]]$deltaAICc) <= 2)
  global_models <- expand.grid(backbone= bb_models,
                               clade1= clade1_models,
                               clade2= clade2_models,
                               clade3= clade3_models)
  joint_logLH <- as.numeric(all_tables[[three_shift[j,1]]]$logLH[global_models$backbone]) + as.numeric(all_tables[[three_shift[j,2]]]$logLH[global_models$clade1]) + as.numeric(all_tables[[three_shift[j,3]]]$logLH[global_models$clade2]) + as.numeric(all_tables[[three_shift[j,4]]]$logLH[global_models$clade3])
                                                                                  # get number of extra parameters for each model:
  bb_extra_par <- sapply(all_tables[[three_shift[j,1]]][, c("alpha", "beta")], function(x) !grepl("NA", x))
  clade1_extra_par <- sapply(all_tables[[three_shift[j,2]]][, c("alpha", "beta")], function(x) !grepl("NA", x))
  clade2_extra_par <- sapply(all_tables[[three_shift[j,3]]][, c("alpha", "beta")], function(x) !grepl("NA", x))
  clade3_extra_par <- sapply(all_tables[[three_shift[j,4]]][, c("alpha", "beta")], function(x) !grepl("NA", x))

  p_sum <- function(x){
    if(length(x) < 3) {
      res <- sum(x)
    } else {
      res <- rowSums(x)
    }
    return(res)
  }
# we always have at least 8 parameters in the simplest BconsDcons model (for backbone and 3 clades); we just need to sum the extra two parameters of each case:
  p_all_models <- 8 +
                  p_sum(bb_extra_par[global_models$backbone,]) +
                  p_sum(clade1_extra_par[global_models$clade1,])  +
                  p_sum(clade2_extra_par[global_models$clade2,]) +
                  p_sum(clade3_extra_par[global_models$clade3,])
  joint_AICc <- sapply(joint_logLH, jointAIC6, p_all_models, Ntip(agave))
  if(!is.null(dim(joint_AICc))){
    joint_AICc <- sapply(joint_logLH, jointAIC6, p_all_models,
                         Ntip(agave))[1,]
  }
  ee <- rep("", length(joint_AICc))  # just to generate empty columns
  global_table <- data.frame(model = ee,
    Backbone = all_tables[[three_shift[j,1]]]$model[global_models$backbone],
    Clade1 = all_tables[[three_shift[j,2]]]$model[global_models$clade1],
    Clade2 = all_tables[[three_shift[j,3]]]$model[global_models$clade2],
    Clade3 = all_tables[[three_shift[j,4]]]$model[global_models$clade3],
    logLH = joint_logLH,
    AICc = joint_AICc,
    deltaAICc = joint_AICc - min(joint_AICc)
  )
  global_table <- global_table[order(global_table$logLH, decreasing = T),]

  cat(sprintf(table_title, count+1,
              clade_names[three_shift[j,2]], clade_names[three_shift[j,3]], clade_names[three_shift[j,4]]))

  print(kable(rbind(all_tables[[three_shift[j,1]]],
                    all_tables[[three_shift[j,2]]],
                    all_tables[[three_shift[j,3]]],
                    all_tables[[three_shift[j,4]]]),
        caption = NULL, row.names = FALSE, booktabs = T) %>%
          group_rows(bb_title[j], 1, 7) %>%
          group_rows(clade1_title[j], 8, 14) %>%
          group_rows(clade2_title[j], 15, 21) %>%
          group_rows(clade3_title[j], 22, 28) # %>%
                    # kable_styling(full_width = TRUE)
  )
  cat("**Global model**", "\n")
  global_table <- my_table_format(global_table)
  print(kable(global_table,
        caption = NULL, row.names = FALSE, booktabs = T) %>%
          row_spec(0, color = c(rep("white", 2), rep("black", 6)))
  )
  cat("\n\n")
  cat(sprintf(figure_title, count+1, 
              clade_names[three_shift[j,2]], clade_names[three_shift[j,3]], clade_names[three_shift[j,4]]))
  plot.divratett(rates = all_tables[[three_shift[j,1]]], 
                 span = c(stem_times[1],0), 
                 x_lim = c(16,0), y_lim = c(y_limA[as.character(count+1)], y_limB[as.character(count+1)]))
  cat("\n\\pagebreak\n")
  count <- count + 1

}

```
